Exercise 3: Software Architecture in Practice Case: Beer Web Store

### 2008-03-17 trunk/SAiP/Module1/H3/doc/architecturaldescription.tex
correction reading

The \emph{uses structure} shows how elements are related with regard
to usage. One perspective of the uses structure is that the
elements in the figure are ``Overview'', ``Basket'' and ``Data''
which are all related and the database which is only related
to ``Data''. This shows that the overview page and the basket
has been decoupled from the database which therefore can be
replaced without affecting them.

@@

Another perspective is that the users, the web server and the
database are elements where the relations show that the users
use the web server and the web server uses the database. This
also shows the that the architecture is a
\emph{strictly layered structure} where the users cannot
access the database directly.

@@

These viewpoints are all relevant to the Beer Web Store example.
The Module viewpoint describes the internals of the web server and how
the functionality is decomposed into units. The Component \& connector
viewpoint describes the runtime relations between the units and the
Allocation viewpoint describes the environment of the running
system.

In the following sections we will give examples on views for each
of the three viewpoints.

@@

Working as an developer/tester/engineer means that everything must be quantifiable in some way, and box-and-line drawings do not offer this unambiguous quantifiable. For this a clearly defined modelling language, without ambiguity as to the meaning of the model, is needed. An example of such a language is Unified Modelling Language(UML), which would allow the box-and-line drawing to be represented as one or more diagrams solving all the ambiguity of the box-and-line drawing with only a single requirement; one must know the language, which is indeed one of the reasons while box-and-line drawings are still widely used - there is no single unambiguous modelling language known by all stakeholders, and when that is the case it may be more confusing then beneficial to spend time making sure the diagram is clear and unambiguous, if that clarity is derived from symbolic notation that the readers (stakeholders) do not understand.

>>>>

The \emph{uses structure} shows how elements are related with regard
to usage. One perspective of the uses structure is that the
elements in the figure are ``Overview'', ``Basket'' and ``Data'',
which are all related and the database, which is only related
to ``Data''. This shows that the overview page and the basket
has been decoupled from the database, which therefore can be
replaced without affecting them.

@@

Another perspective is that the users, the web server and the
database, are elements where the relations show that the users
use the web server and the web server uses the database. This
also shows the that the architecture is a
\emph{strictly layered structure} where the users cannot
access the database directly.

@@

These viewpoints are all relevant to the Beer Web Store example.
The Module viewpoint describes the internals of the web server and how
the functionality is decomposed into units. The Component \& Connector
viewpoint describes the runtime relations between the units and the
Allocation viewpoint describes the environment of the running
system.

In the following sections we will give examples of views for each
of the three viewpoints.

@@

Working as a developer/tester/engineer means that everything must be quantifiable in some way, and box-and-line drawings do not offer this unambiguous quantifiability. For this a clearly defined modelling language, without ambiguity as to the meaning of the model, is needed. An example of such a language is Unified Modelling Language (UML), which would allow the box-and-line drawing to be represented as one or more diagrams solving all the ambiguity of the box-and-line drawing with only a single requirement; one must know the language, which is indeed one of the reasons while box-and-line drawings are still widely used - there is no single unambiguous modelling language known by all stakeholders, and when that is the case it may be more confusing then beneficial to spend time making sure the diagram is clear and unambiguous, if that clarity is derived from symbolic notation that the readers (stakeholders) do not understand.
